### 2020-12-10 paper/localpsf.tex
literature review gah

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used as an estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. For example, if the width of $\varphi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size.
%in which the length scales of the functions $\varphi_x$ are estimated for all $x$ simultaneously by applying $\mathcal{A}^T$ to a small number of random noise functions, $\zeta$, and post-processing the results. 
In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method estimates the support of $\varphi_p$ more accurately than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

Use for approximating Hessians in PDE-constrained optimization: Georg's paper, my paper.

H-matrices for Hessians: Ilonas paper with KAUST people

>>>>

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used as an estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. For example, if the width of $\varphi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size. In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method estimates the support of $\varphi_p$ more accurately than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

A product-convolution type approximation of the Hessian in a seismic imaging problem was used in [CITE GEORG].

Conventional H-matrix construction methods require access to matrix entries of the matrix being approximated, and therefore cannot be used to efficiently form H-matrix approximations of operators that are only available through matrix-vector products. There are matrix-free methods for H-matrix approximation [CITE LEXING PAPER, CITE MARTINSSON, CITE OTHERS], and these methods have been used to form H-matrix compressions of Hessians in PDE constrained inverse problems [CITE ILONA, CITE NOEMI/TUCKER HODLR]. While these matrix-free H-matrix construction methods are asymptotically scalable in theory, the required number of matrix vector products is large in practice.

%H-matrices for Hessians: Ilonas paper with KAUST people
